Supplementary materials for the paper ``Uncertainty propagation in neural networks for sparse coding''

### 2018-05-14 paper/supplementary.tex
supplementary added time

\section{Posterior estimation for the \textsc{mnist} data}
Figure~\ref{fig:posterior_samples} shows samples from the posterior for one of the validation data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.

@@

>>>>

\section{Additional results on the \textsc{mnist} data}
In contrast to \textsc{lista} and baselines, the Bayesian \textsc{lista} provides a posterior estimate. Figure~\ref{fig:posterior_samples} shows samples from the posterior for one of the test data points and Figure \ref{fig:posterior_distribution} shows the parameters of this posterior.

@@

Here we also provide the comparison of the Bayesian and non-Bayesian \textsc{lista} networks in terms of the clock time (Figure ).
